Viscous Transport in Eroding Porous Media

### 2019-06-03 docs/transport/erosion_transport.tex
do the result section in transport paper

In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect of the geometrical structure on fluid velocity field. In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the x-component velocity u(-1, y) to its maximum velocity, namely, $u_{max}=6.2281 \times 10^{-4}$ at equal spreading tracers on the cross section at x=-1 and y in [-1,1]. The velocity is continuous along the cross section and acting as several Poiseuille flows. This velocity graph is different from the one in~\cite{matyka2008tortuosity} since we choose our cross section to be the beginning of the flow before the fluid touches any body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuousity $\tau$ of the tracers at the cross section. This graph is not continuous and the jumps in $\tau$ mean that the initial neighbor tracers have been seperated by the bodies.

>>>>

In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect of the geometrical structure on fluid velocity field. In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281 \times 10^{-4}$ at equal spreading tracers on the cross section (x=-1 and y in [-1,1]). The velocity is continuous along the cross section and acting as several Poiseuille flows. This velocity graph is different from the one in~\cite{matyka2008tortuosity} since we choose our cross section to be the beginning of the flow before the fluid touches any body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuousity $\tau$ of the tracers at the cross section. This graph is not continuous and the jumps in $\tau$ mean that the initial neighbor tracers have been seperated by the bodies.
